---
title: "GroupHW"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Marketing Mix Model

Read data file
```{r echo=FALSE, include=FALSE}
library(tidyverse)
library(lfe)
library(stargazer)

```


### Section 1

In this section, we clean the data before feeding it into the regression models. We log-transform ad metrics, competitor ad metrics, and brand attitude metrics using the log of (x+1). We then create 13 lag variables for each brand attitude metric. We also create 5 lags for each advertising spend metric (both own brand and competitor). We then drop the first 13 observations for each brand, since the lagged brand attitude metrics contain NAs during the first 13 weeks of the data.

```{r echo=TRUE}

#1.

dat <- read_csv("randomized_data_for_hw.csv")

#3.

dat <- dat %>% mutate(nat=log(nat+1), loc=log(loc+1), dig=log(dig+1), 
                      compnat=log(compnat+1), comploc=log(comploc+1), compdig=log(compdig+1), 
                      qua=log(qua+1), val=log(val+1), sat=log(sat+1))

#4.

dat <- dat %>% mutate(nat=log(nat+1), loc=log(loc+1), dig=log(dig+1), 
                      compnat=log(compnat+1), comploc=log(comploc+1), compdig=log(compdig+1), 
                      qua=log(qua+1), val=log(val+1), sat=log(sat+1))



dat <- dat %>% group_by(Brand) %>% mutate(lag1qua=lag(qua, n=1), lag2qua=lag(qua, n=2), 
                                          lag3qua=lag(qua,n=3), lag4qua=lag(qua,n=4), 
                                          lag5qua=lag(qua,n=5), lag6qua=lag(qua,n=6), 
                                          lag7qua=lag(qua,n=7), lag8qua=lag(qua,n=8),
                                          lag9qua=lag(qua,n=9), lag10qua=lag(qua,n=10),
                                          lag11qua=lag(qua,n=11), lag12qua=lag(qua,n=12), 
                                          lag13qua=lag(qua,n=13))

dat <- dat %>% group_by(Brand) %>% mutate(lag1val=lag(val, n=1), lag2val=lag(val, n=2), 
                                          lag3val=lag(val,n=3), lag4val=lag(val,n=4), 
                                          lag5val=lag(val,n=5), lag6val=lag(val,n=6), 
                                          lag7val=lag(val,n=7), lag8val=lag(val,n=8),
                                          lag9val=lag(val,n=9), lag10val=lag(val,n=10),
                                          lag11val=lag(val,n=11), lag12val=lag(val,n=12), 
                                          lag13val=lag(val,n=13))

dat <- dat %>% group_by(Brand) %>% mutate(lag1sat=lag(sat, n=1), lag2sat=lag(sat, n=2), 
                                          lag3sat=lag(sat,n=3), lag4sat=lag(sat,n=4), 
                                          lag5sat=lag(sat,n=5), lag6sat=lag(sat,n=6), 
                                          lag7sat=lag(sat,n=7), lag8sat=lag(sat,n=8),
                                          lag9sat=lag(sat,n=9), lag10sat=lag(sat,n=10),
                                          lag11sat=lag(sat,n=11), lag12sat=lag(sat,n=12), 
                                          lag13sat=lag(sat,n=13))


#5.

dat <- dat %>% group_by(Brand) %>% mutate(lag1nat=lag(nat, n=1), lag2nat=lag(nat, n=2), 
                                          lag3nat=lag(nat,n=3), lag4nat=lag(nat,n=4), 
                                          lag5nat=lag(nat,n=5))

dat <- dat %>% group_by(Brand) %>% mutate(lag1loc=lag(loc, n=1), lag2loc=lag(loc, n=2), 
                                          lag3loc=lag(loc,n=3), lag4loc=lag(loc,n=4), 
                                          lag5loc=lag(loc,n=5))

dat <- dat %>% group_by(Brand) %>% mutate(lag1dig=lag(dig, n=1), lag2dig=lag(dig, n=2), 
                                          lag3dig=lag(dig,n=3), lag4dig=lag(dig,n=4), 
                                          lag5dig=lag(dig,n=5))

dat <- dat %>% group_by(Brand) %>% mutate(lag1compnat=lag(compnat, n=1), lag2compnat=lag(compnat, n=2), 
                                          lag3compnat=lag(compnat,n=3), lag4compnat=lag(compnat,n=4), 
                                          lag5compnat=lag(compnat,n=5))

dat <- dat %>% group_by(Brand) %>% mutate(lag1compdig=lag(compdig, n=1), lag2compdig=lag(compdig, n=2), 
                                          lag3compdig=lag(compdig,n=3), lag4compdig=lag(compdig,n=4), 
                                          lag5compdig=lag(compdig,n=5))

dat <- dat %>% group_by(Brand) %>% mutate(lag1comploc=lag(comploc, n=1), lag2comploc=lag(comploc, n=2), 
                                          lag3comploc=lag(comploc,n=3), lag4comploc=lag(comploc,n=4), 
                                          lag5comploc=lag(comploc,n=5))
#6

dat <- dat %>%
  group_by(Brand) %>%
  slice(14:n())

```




### Section 2

After completing data preparation, now we can build the du-joo-wilbur Quality regressions and coefficient estimates.

re1 - We regress quality on each of the 3 ad metrics, including 5 lags of each of the 3 ad metrics,
5 lags of each of the competitor ad metrics, 13 lags of each of the brand attitude metrics,
week fixed effects and brand fixed effects. 

re2 - Using the same regression equation in re1, we use the felm command from the lfe
package. 

re3 - In re2, we weight the data by qua_vol.

re4 - In re3, we replace the brand fixed effects with brand-quarter fixed effects. 

re5 - In re4, we replace the week fixed effects with industry-week fixed effects.

```{r echo=TRUE}


#1.
re1 <- lm(qua~nat + loc + dig + lag1qua   +  lag2qua   +  lag3qua  +   lag4qua    +
            lag5qua  +   lag6qua   +  lag7qua   +  lag8qua  +   lag9qua    + lag10qua  +  lag11qua  +  lag12qua  +  lag13qua +  
            lag1val   +  lag2val +    lag3val +    lag4val    + lag5val    + lag6val  +   lag7val +    lag8val  +   lag9val  +  
            lag10val  +  lag11val    +lag12val +   lag13val  +  lag1sat   +  lag2sat   +  lag3sat +    lag4sat  +   lag5sat   + 
            lag6sat   +  lag7sat   +  lag8sat   +  lag9sat   +  lag10sat   + lag11sat  +  lag12sat   + lag13sat    +lag1nat   + 
            lag2nat   +  lag3nat   +  lag4nat  +   lag5nat   +  lag1loc   +  lag2loc    + lag3loc    + lag4loc    + lag5loc  +  
            lag1dig +    lag2dig   +  lag3dig+     lag4dig  +   lag5dig +    lag1compnat  +lag2compnat  +lag3compnat+  lag4compnat +
            lag5compnat  +lag1comploc+ lag2comploc +lag3comploc +lag4comploc +lag5comploc+ lag1compdig+ lag2compdig +lag3compdig+
            lag4compdig+ lag5compdig + as.factor(Brand) + as.factor(time_period), data=dat)

#2.

re2 <- felm(qua~nat + loc + dig + lag1qua   +  lag2qua   +  lag3qua  +   lag4qua    +
              lag5qua  +   lag6qua   +  lag7qua   +  lag8qua  +   lag9qua    + lag10qua  +  lag11qua  +  lag12qua  +  lag13qua +  
              lag1val   +  lag2val +    lag3val +    lag4val    + lag5val    + lag6val  +   lag7val +    lag8val  +   lag9val  +  
              lag10val  +  lag11val    +lag12val +   lag13val  +  lag1sat   +  lag2sat   +  lag3sat +    lag4sat  +   lag5sat   + 
              lag6sat   +  lag7sat   +  lag8sat   +  lag9sat   +  lag10sat   + lag11sat  +  lag12sat   + lag13sat    +lag1nat   + 
              lag2nat   +  lag3nat   +  lag4nat  +   lag5nat   +  lag1loc   +  lag2loc    + lag3loc    + lag4loc    + lag5loc  +  
              lag1dig +    lag2dig   +  lag3dig+     lag4dig  +   lag5dig +    lag1compnat  +lag2compnat  +lag3compnat+  lag4compnat +
              lag5compnat  +lag1comploc+ lag2comploc +lag3comploc +lag4comploc +lag5comploc+ lag1compdig+ lag2compdig +lag3compdig+
              lag4compdig+ lag5compdig | as.factor(Brand) + as.factor(time_period), data=dat)

#3.

re3 <- felm(qua~nat + loc + dig + lag1qua   +  lag2qua   +  lag3qua  +   lag4qua    +
              lag5qua  +   lag6qua   +  lag7qua   +  lag8qua  +   lag9qua    + lag10qua  +  lag11qua  +  lag12qua  +  lag13qua +  
              lag1val   +  lag2val +    lag3val +    lag4val    + lag5val    + lag6val  +   lag7val +    lag8val  +   lag9val  +  
              lag10val  +  lag11val    +lag12val +   lag13val  +  lag1sat   +  lag2sat   +  lag3sat +    lag4sat  +   lag5sat   + 
              lag6sat   +  lag7sat   +  lag8sat   +  lag9sat   +  lag10sat   + lag11sat  +  lag12sat   + lag13sat    +lag1nat   + 
              lag2nat   +  lag3nat   +  lag4nat  +   lag5nat   +  lag1loc   +  lag2loc    + lag3loc    + lag4loc    + lag5loc  +  
              lag1dig +    lag2dig   +  lag3dig+     lag4dig  +   lag5dig +    lag1compnat  +lag2compnat  +lag3compnat+  lag4compnat +
              lag5compnat  +lag1comploc+ lag2comploc +lag3comploc +lag4comploc +lag5comploc+ lag1compdig+ lag2compdig +lag3compdig+
              lag4compdig+ lag5compdig | as.factor(Brand) + as.factor(time_period), data=dat, weights = dat$qua_vol)

#4.

re4 <- felm(qua~nat + loc + dig + lag1qua   +  lag2qua   +  lag3qua  +   lag4qua    +
              lag5qua  +   lag6qua   +  lag7qua   +  lag8qua  +   lag9qua    + lag10qua  +  lag11qua  +  lag12qua  +  lag13qua +  
              lag1val   +  lag2val +    lag3val +    lag4val    + lag5val    + lag6val  +   lag7val +    lag8val  +   lag9val  +  
              lag10val  +  lag11val    +lag12val +   lag13val  +  lag1sat   +  lag2sat   +  lag3sat +    lag4sat  +   lag5sat   + 
              lag6sat   +  lag7sat   +  lag8sat   +  lag9sat   +  lag10sat   + lag11sat  +  lag12sat   + lag13sat    +lag1nat   + 
              lag2nat   +  lag3nat   +  lag4nat  +   lag5nat   +  lag1loc   +  lag2loc    + lag3loc    + lag4loc    + lag5loc  +  
              lag1dig +    lag2dig   +  lag3dig+     lag4dig  +   lag5dig +    lag1compnat  +lag2compnat  +lag3compnat+  lag4compnat +
              lag5compnat  +lag1comploc+ lag2comploc +lag3comploc +lag4comploc +lag5comploc+ lag1compdig+ lag2compdig +lag3compdig+
              lag4compdig+ lag5compdig | as.factor(Brand) + as.factor(yrqtr) + as.factor(time_period), data=dat, weights = dat$qua_vol)

#5

re5 <- felm(qua~nat + loc + dig + lag1qua   +  lag2qua   +  lag3qua  +   lag4qua    +
              lag5qua  +   lag6qua   +  lag7qua   +  lag8qua  +   lag9qua    + lag10qua  +  lag11qua  +  lag12qua  +  lag13qua +  
              lag1val   +  lag2val +    lag3val +    lag4val    + lag5val    + lag6val  +   lag7val +    lag8val  +   lag9val  +  
              lag10val  +  lag11val    +lag12val +   lag13val  +  lag1sat   +  lag2sat   +  lag3sat +    lag4sat  +   lag5sat   + 
              lag6sat   +  lag7sat   +  lag8sat   +  lag9sat   +  lag10sat   + lag11sat  +  lag12sat   + lag13sat    +lag1nat   + 
              lag2nat   +  lag3nat   +  lag4nat  +   lag5nat   +  lag1loc   +  lag2loc    + lag3loc    + lag4loc    + lag5loc  +  
              lag1dig +    lag2dig   +  lag3dig+     lag4dig  +   lag5dig +    lag1compnat  +lag2compnat  +lag3compnat+  lag4compnat +
              lag5compnat  +lag1comploc+ lag2comploc +lag3comploc +lag4comploc +lag5comploc+ lag1compdig+ lag2compdig +lag3compdig+
              lag4compdig+ lag5compdig | as.factor(Brand)+ as.factor(yrqtr)+ as.factor(Industry) +as.factor(time_period), data=dat, weights = dat$qua_vol)




```


We create a pretty table that shows advertising coefficient estimates for  regressions 2, 3, 4, and 5
side by side. We also omit the lagged brand attitude coefficient estimates in the table.


```{r echo=TRUE}
#6


pretty_table <- stargazer(re2, re3, re4,re5 , type="text",
          title="Regression Results",  omit = rownames(re2$coefficients)[4:42], out = 'tab.html', 
          column.labels = c('Model1','Model2','Model3','Model4'), model.numbers = FALSE, 
          dep.var.caption = 'Percieved Quality')


```
